
\cvsection{Education}
\cvevent{National Research University Higher School of Economics}{Applied Mathematics and Informatics - GPA 8.86/10}{ Sep 2019 -- Currently}{}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Chat-bot For Client's Mood Improvement}
\begin{itemize}
\item My course work - Transfromer-based chat-bot, aimed to communicate with clients on some abstract themes. It is maid using PyTorch and some other python frameworks. It is still in progress.
\end{itemize}
\smallskip
\smallskip
\cvproject{Business Placing Helper}
\begin{itemize}
\item Find good enough place for your cafe or sun glasses shop in such big city as Moscow is not very easy. Here goes this project: we recommend better places for different kinds of business using machine learning and open city data. This project is also in progress.
\end{itemize}
\smallskip
\smallskip
\cvproject{Auto Linear Algebra Solver}
\begin{itemize}
\item Linear Algebra includes a lot of monotonous calculations. For this reason I decided to make python script, which could solve matrix equations and print process of solution in LaTeX. This project made my life much easier.
\end{itemize}
\smallskip
\smallskip
\cvproject{Custom Hash Map Implementation}
\begin{itemize}
\item Fully functional custom implementation of std::unordered\_map (C++).
\end{itemize}
